\section*{Motivation}
Why is it interesting?
The project is being worked on in collaboration with Dalux which is a software company that makes BIM models (Building information modelling). At the moment Dalux has to hire an expensive arcitect to walk around the construction site to check up on that everything is going according to plan and that there aren’t any errors. If this process could be automated such that a robot could walk around a construction instead and send the data directly to Dalux’ software, that would be of great benefit for Dalux. 


\section{Abstract}
Første problem. En bim model ind og finde fra a til b.
\begin{itemize}
    \item Make a simulation of a particle moving from one point to another
    \item Make the simulation include walls and obstacles
    \item Transfer walls from a real BIM model onto simulation
    \item Make a maximum coverage algorithm to find specific nodes that are most optimal for point clouds
    \item Find an optimal route for the particle to move between maximum coverage nodes.
    \item Start testing on the robot and include 
\end{itemize}



\section*{Objective}
The objective of this project is to program the spot robot from Boston Dynamics
to move around construction sites. The robot should be able to walk around the entire construction site on its own and should – while walking – take pictures (or/and point scans) of the construction site. The purpose of this is that after the construction workers have done their day of work the spot robot should wake up at night and walk around the construction site to see if everything is going according to plan and if all deadlines and milestones are met.

What should be done?
Boundaries: what can I probably not do?
Risk analysis: What parts of the project are going to be difficult



\section*{Previous work}

\section*{Introduction}
Explain what you’re going to do

\section*{Literature review}
(Write about what the field around your research looks like)

\section*{Dataset}
Describe your dataset(s), including literature relevant to that dataset, if any

\section*{Results}
(Tell us what you have found)

\section*{Conclusion}
(Summarize your findings, bring in perspectives)
Notes on what works and didn’t work:

\section*{Litteratur list}


\section{Svar på spm}
\subsection{Skal jeg skrive i passiv eller aktiv form?}
The project is being worked on in collaboration with...
I am working on the project in collaboration with…
\\\\
Brug aktiv form. En gang på siden bruge “I”.
Som regel inkluderer man læseren og bruger “We”, hvis det er noget du har lavet så “I”.
Tit bruger man ikke personer som subjekt.
Brug mest aktiv, der må gerne være lidt passivt.


Gulv areal hvert pixel bliver et grid punk. Skyd en email hvis du løbetr ind i problemer.
Unity reflect det der oversætter bim modeller til unity. Hen ad vejen måske.
Ray trace bim model der kunen hjælpe med at finde ud af fra et punkt til et andet.


