\section{Different sections to write about}

\subsection{Previous work}
\begin{itemize}
    \item Write about the 3 week project Gwayfinding
\end{itemize}

\subsection{Litteratur review}
\begin{itemize}
    \item Write about the paper that explains people pathfinding in building, where they use grid instead of polygonal
    \item Write about pathfinding in 2d world master thesis. How they describe the difference between polygonal and grid, what algorithms to use for each etc.
    \item Write about the TSP problem, and its solutions. Find paper for that perhaps.
    \item Maybe find paper about Spot.
\end{itemize}


\subsection{Plotting floorplans}
\begin{itemize}
    \item Section about preprocessing of the dataset
    \item Section about the data and the polygonal triangle structure of the dataset, and why it makes sense.
    \item Talk about removing redundant lines from triangles.
    \item Talk about the challenges of plotting the doors. How I did this manually instead.
\end{itemize}

\subsection{Grid vs polygonal}
\begin{itemize}
    \item Talk about how you could use the grid version or the polygonal version. Spent a good amount of effort here.
\end{itemize}

\subsection{Which platform to use}
\begin{itemize}
    \item Write about which platform to use. The pros and cons of each. Ros vs Unity vs Python.
\end{itemize}


\subsection{TSP}
\begin{itemize}
    \item How to represent nodes and graphs? Comparison of different ways and libraries
    \item Making a weighted graph of all the nodes, where the weights are the Euclidean distance between each node. Write that it is a undirected graph.
    \item A section on the line intersection algorithm used for connecting the points
    \item Using dijkstra's/A* to make a complete subgraph of all the relevant nodes, and how this problem is a bit different than the traditional tsp.
    \item A section of the 2-OPT algorithm and how it uses Minimum Spanning Tree and a DFS traversal. You can talk about alternative algorithms and ther pros and cons.
    \item A section describing the MST and DFS algorithms and how Networkx implementation work. Maybe a section about adjacency list vs matrix, kruskal vs prims. When to use which.
\end{itemize}

\subsection{Dimensions of robot}
\begin{itemize}
    \item Write about how to incorporate the dimensions of the robot in your simulation
\end{itemize}

\subsection{Optimal placement of nodes}
\begin{itemize}
    \item Write about scenic route vs discrete points.
    \item Write about SLAM
    \item optimal placement of nodes
\end{itemize}

\subsection{Spot}
\begin{itemize}
    \item Write about Spot and how it is a usefull robot for this thesis
    \item Write about different platforms for programming Spot, python API vs ROS.
\end{itemize}

\subsection{Future work}
\begin{itemize}
    \item A section about stairs
\end{itemize}